Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Undo some of mstone's parallel structure, sorry.

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}. Nell takes advantage of this fact 
to augment prior affordances for \textit{action}, \textit{reflection}, and
\textit{communication} with new affordances for \textit{engagement} in the form of
a modular \textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}.
In this interface, all system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with one of the
system protagonists.

@@

Children grow. To accommodate them, Nell provides a ``low floor and
no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially exposing story modules to tackle topics of
increasing difficulty.  Later, the ability for third
parties to independently author story modules ensures that
Nell can continue to grow.  Finally, there are no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

@@

Children often learn from direct interactive experience. Consequently, Nell
intensifies our commitment to constructionism~\cite{Papert91} by further
emphasizing creation and tangible interaction using a tablet computer as a way
to maintain the child's connection to their work (Fig.~\ref{fig:xo3}).

@@

\subsection{Handwriting recognition}
To support \textit{direct interaction}, we use a separated-character
handwriting recognition engine based on Hidden Markov Models~\cite{hanshu:handwriting}.

@@

>>>>

Experience with our previous educational software
system has shown gratifying uptake and
use by children.  But we are often disappointed that some of our
favorite pedagogical tools included in the systems were not being
widely used.  Enthusiastic teachers would spark intensive use in
certain classrooms, but children had difficulty finding their way into
the material without strong guidance.

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}.  Nell uses a
\textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}
to guide the child user through the pedagogical capabilities of the
system. 
In this interface, all system actions are shaped by a storybook metaphor, and
interactions with the system are conceptualized as interactions with one of the
system protagonists.

@@

Children grow. To accommodate them, Nell provides a ``low floor and
no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The serial progression of story modules grows with
the child to tackle topics of increasing difficulty.
Later, the ability for third
parties to independently author story modules ensures that
Nell can continue to grow.  Finally, there are no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

@@

%MSTONE PARALLEL STRUCTURE:
%Children often learn from direct interactive experience. Consequently, Nell
%intensifies our commitment to constructionism~\cite{Papert91} by further
%emphasizing creation and tangible interaction using a tablet computer as a way
%to maintain the child's connection to their work (Fig.~\ref{fig:xo3}).

The constructionist learning philosophy emphasizes creation and
tangible interaction.  Nell uses direct interaction on a tablet
computer to maintain the child's connection to their work
(Fig.~\ref{fig:xo3}).

@@

@@

% MSTONE TEXT
% Nell takes advantage of this fact 
% to augment prior affordances for \textit{action}, \textit{reflection}, and
% \textit{communication} with new affordances for \textit{engagement} in the form of
% a modular \textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}.
